---
title: "Reading data from the internet"
author: "Felix Tran"
date: "October 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)

```

# Scrape a table from the table
Using read_html() from the rvest package, we can scrape table information from
a webpage
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_xml <- read_html(url)
drug_use_xml
```

Knowing how html is formatted with CSS styling, we can narrow our focus to 
certain aspects of the webpage (i.e. the stuff in tables)

To look only at the first table, we use the syntax for lists to get the 1st 
table. Convert that information into a dataset with html_table(), then remove
the first row bc it is just notes about the table in this case using slice(). 
Convert the dataset into a tibble, and we have extracted the data.
```{r}
drug_use_xml %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table() %>% 
  slice(-1) %>% 
  as_tibble()
```


Exercise - Read a table from a website about cost of living in NYC
```{r}
url <- "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"
ny_xml <- read_html(url)

ny_xml %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>% 
  html_table(header = T)

```

# Harry Potter
Using the SelectorGadget tool, we can extract specific information from websites
which aren't formatted very well
```{r}
hp_titles <- read_html("https://www.imdb.com/list/ls000630791/") %>% 
  html_nodes(css = ".lister-item-header a") %>% 
  html_text()
hp_titles

hp_money <- read_html("https://www.imdb.com/list/ls000630791/") %>% 
  html_nodes(css = ".text-small:nth-child(7) span:nth-child(5)") %>% 
  html_text()

hp_df <- tibble(
  title = hp_titles,
  gross_rev = hp_money
)

```


# Working with API
Get data on water consumption in NYC (CSV)
```{r}
nyc_water <- GET("https://data.cityofnewyork.us/resource/waf7-5gvc.csv") %>% 
  content("parsed")
```

Same as above but with JSON
```{r}
nyc_water <- GET("https://data.cityofnewyork.us/resource/waf7-5gvc.json") %>% 
  content("text") %>% 
  jsonlite::fromJSON() %>% 
  as_tibble()
nyc_water
```



```{r}

```

